\input{includes/assignment_preamble}

\def\AssignmentCourse{AP Computer Science A}
\def\AssignmentNumber{06}
\def\AssignmentTitle{Strings}

\begin{document}
  \begin{questions}
    \BlueQuestion{What does the following code fragment print?}
      \begin{lstlisting}
        String string1 = "Hello";
        String string2 = string1;
        string1 = "World!";
        System.out.println(string1);
        System.out.println(string2);
      \end{lstlisting}

    \BlueQuestion{Given a string \code{site} that represents the URL for a website, write a code fragment to determine its top-level domain (TLD). For example, the TLD for the string \code{"http://www.woodstockschool.in"} is: \code{in}.}

    \GreenQuestion{\code{String} values are \emph{immutable} in Java. That is, every time a specific \code{String} is used (whether stored in a variable or used as a \code{String} literal) the \emph{same} \code{String} in memory is referenced. Many other programming languages, such a Python, use a similar scheme for the storage of \code{String} values. Explain the benefits of this approach.}

    \GreenQuestion{A string, \code{s}, is a \emph{circular shift} of a string, \code{t}, if it matches when the characters are circularly shifted by any number of positions. For example, \code{ACTGACG} is a circular shift of \code{TGACGAC} and vice versa. Detecting this condition is important in the study of genomic sequences. Write a method that checks whether two given strings, \code{s} and \code{t}, are circular shifts of one another.}\\[4pt]{\small\textbf{Note:} This can be accomplished using a very simple technique involving string concatenation.}
    \YellowQuestion{\emph{Password Strength Verification.} Write a static method that takes a single, \code{String} argument and returns \code{true} if it meets all of the following conditions and \code{false} otherwise.}
      \begin{itemize}
        \item The string is at least $8$ characters in length.
        \item The string contains at least one numeric digit (0--9).
        \item The string contains at least one upper-case letter.
        \item The string contains at least one lower-case letter.
      \end{itemize}

    \RedQuestion{\emph{Kama Sutra Cipher.} The \emph{Kama Sutra} describes a fairly simple encryption technique (listed as the ``art of secret writing''). It requires a one-to-one pairing of letters. A message can then be encoding by replacing every letter with its pair.}\\[4pt]
    {\small\textbf{Example:} Suppose that the following table of pairings were being used:
      \begin{center}
        \renewcommand\arraystretch{1.5}
        \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c |}
          \hline
          T & H & E & Q & U & I & C & K & B & R & O & W & N\\
          \hline
          F & X & J & M & P & S & V & L & A & Z & Y & D & G\\
          \hline
        \end{tabular}
      \end{center}
    Then, the message ``MEET AFTER SCHOOL'' would be encoded as: ``QJJF BTFJZ IVXYYK''.

    Often, the pairings will be recorded as a series of keywords which are then used to create the table of pairings. (In the above example, the two keywords are: ``THEQUICKBROWN'' and ``FXJMPSVLAZYDG''.)}

    Create a method, \code{KamaSutra()}, that will take three, \code{String} parameters: the first parameter is the text to be encoded and the remaining two parameters are the two keywords for a Kama Sutra cipher. The method should return the enciphered text.\\
    {\small\textbf{Note:} Treat as a precondition that the keywords are of equal length and contain no duplicate letters.}
  \end{questions}
\end{document}
