\input{includes/assignment_preamble}

\def\AssignmentCourse{AP Computer Science A}
\def\AssignmentNumber{12}
\def\AssignmentTitle{The Linked List}

\begin{document}
  \begin{questions}
    \BlueQuestion{Explain at least one benefit and one drawback for using a linked list in place of a traditional array in the \code{Stack} and \code{Queue} data structures.}

    \BlueQuestion{Implement the \code{trimN()} method in our \code{LinkedList} class. This method should take \code{N} as a parameter and remove the last \code{N} nodes from the list.}

    \GreenQuestion{Implement \code{Queue} using a linked list. Ensure you maintain the use of generics as appropriate.}

    \GreenQuestion{Implement the \code{find()} method in our \code{LinkedList} class. This method should take some data, \code{key}, as a parameter and return the index where \code{key} exists as the data for a particular \code{Node}. This method should return the value $-1$ if \code{key} does not exist in the linked list.}

    \YellowQuestion{\emph{Doubly-Linked List.} Make all necessary changes to our \code{LinkedList} in order to implement a \emph{doubly-linked list} in which each node has both \code{Next} and \code{Previous} attributes. In particular, ensure that \code{add()} and \code{remove()} work as intended.}

    \RedQuestion{\emph{Deque.} A double-ended queue or \emph{deque} (pronounded ``deck'') is like a stack of a queue but supports adding and removing items from both ends. A deque stores a collection of items and supports the following operations:}
      \begin{center}
        \small
        \begin{tabular}{p{0.33\textwidth} r}
          \code{isEmpty()} & is the deque empty?\\
          \code{size()} & how many items are in the deque?\\
          \code{pushLeft(item)} & add an item to the left end\\
          \code{pushRight(item)} & add an item to the right end\\
          \code{popLeft()} & remove and return an item from the left end\\
          \code{popright()} & remove and return an item from the right end
        \end{tabular}
      \end{center}
    Implement a \emph{deque} in Java using a doubly-linked list.
  \end{questions}
\end{document}
