\input{includes/assignment_preamble}

\def\AssignmentCourse{AP Computer Science A}
\def\AssignmentNumber{01}
\def\AssignmentTitle{Variables \& Operations}

\begin{document}
  \begin{questions}
    \BlueQuestion{Give the value of \code{a} after the execution of each of the following sequences.}
      \begin{parts}
        \part
          \begin{lstlisting}
            int a = 1;
            a = a + a;
            a = a + a;
            a = a + a;
          \end{lstlisting}

        \part
          \begin{lstlisting}
            double a = 2;
            a = a * a;
            a = a * a;
            a = a * a;
          \end{lstlisting}

        \part
          \begin{lstlisting}[]
            boolean a = true;
            a = !a;
            a = !a;
            a = !a;
          \end{lstlisting}
      \end{parts}

    \BlueQuestion{Why does \code{10 / 3} result in the value \code{3} instead of \code{3.33333333}? What modifications would you need to make to ensure the value \code{3.33333333}?}

    \GreenQuestion{What do each of the following print?}
      \begin{parts}
        \part \code{System.out.println(2 + "bc");}
        \part \code{System.out.println(2 + 3 + "bc");}
        \part \code{System.out.println((2 + 3) + "bc");}
        \part \code{System.out.println("bc" + (2 + 3));}
        \part \code{System.out.println("bc" + 2 + 3);}
      \end{parts}

    \GreenQuestion{A physics student gets unexpected results when using the code:}
      \begin{center}
        \code{F = G * mass1 * mass2 / r * r;}
      \end{center}
    to compute values according to the formula $F = Gm_{1}m_{2}/r^{2}$. Explain the problem with the code and indicate how you would fix it.

    \YellowQuestion{\emph{Rolling Dice.} Write a program that generates and prints two random integers between $1$ and $6$ (as if you were rolling dice).}\\[4pt]{\small\textbf{Hint:} You can use \code{Math.random()} to generate a random number. Experiment with its output before deciding how you can use it to restrict your values to the desired results.}

    \RedQuestion{\emph{Loan Payments.} Write a program that calcualtes the monthly payments you would have to make over a given number of years to pay off a loan at a given interest rate, compounded continuously. Given the number of years, $t$, the principal, $P$, and the annual interest rate, $r$, the total amount paid at the end of a loan is given by the formula: $A = Pe^{rt}$.}\\[4pt]{\small\textbf{Hint:} Use \code{Math.exp(n)} to calculate $e^{n}$.}
  \end{questions}
\end{document}
